Analysis of bulk void regions

### 2014-05-12 cosmic_voids.tex
Some corrections, adding introduction to section of properties of voids

The first important conclusion is regarding the distribution of the FA 
index, where there is an almost perfect correlation with the $\lambda_1$ 
eigenvalue for low values of it. This result can be interpreted as an 
one-dimensional tomography of void regions, where low $\lambda_1$ values 
are associated to the central regions of voids and they are the more 
isotropic structures found, with FA values close to 0. As we increase the 
$\lambda_1$ value, corresponding to progressively outer layers of void 
regions or less isotropic voids, the FA index increases as well, 
maintaining a very reliable correlation approximately until $FA=0.95$. 
This limit value of the FA can be traduced in terms of an optimal \lth, 
where we obtain $\lambda_{opt}^V = 0.175$ for the V-web scheme and 
$\lambda_{opt}^T = 0.265$ for the T-web scheme, both values consistent 
with optimal thresholds normally taken in previous works \SRKED{[references]}. 
Due to the definition of the fractional anisotropy index, it presents the 
highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$.
Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
FA limit, such that the outer regions of voids becomes highly anisotropic, 
it would imply that voids are invading filaments and sheets, so the 
optimal \lth value is a limit value up to which we can have void regions. 
For other type of environment such as sheets, filaments and knots, the 
$\lambda_1$ eigenvalue does not control their spatial boundaries, so the 
correlation with the FA index is no longer valid beyond the threshold 
values, furthermore the larger dispersion of the FA distribution also 
indicates that contours of the FA field are no longer corresponding to 
contours of the $\lambda_1$ field. Nevertheless, for high $\lambda_1$ 
values, i.e. $\lambda_1>1.0$, the median value of the FA index decreases 
to lower values, indicating the presence of isotropic knots. All of this 
allows us to conclude that the distribution of the FA with respect to the 
$\lambda_1$ eigenvalue is not only an one-dimensional tomography of voids, 
but also a sort of one-dimensional projection of the global structure of 
the cosmic web, starting in highly isotropic central voids, passing 
through very anisotropic sheets and filaments, until isotropic knot 
regions.

@@

Once defined the proper scheme to classify bulk voids in the simulation,
we proceed to analyse their physical properties, like the inertia values,
the density and peculiar velocities profiles as calculated over the grid 
and profiles of number of halos.

>>>>

The first important conclusion is regarding the distribution of the FA 
index, where there is an almost perfect correlation with the $\lambda_1$ 
eigenvalue for low values of it. This result can be interpreted as an 
one-dimensional tomography of void regions, where low $\lambda_1$ values 
are associated to the central regions of voids, these being the most 
isotropic structures found, with FA values close to 0. As we increase the 
$\lambda_1$ value, corresponding to progressively outer layers of void 
regions or less isotropic voids, the FA index increases as well, 
maintaining a very reliable correlation approximately until $FA=0.95$. 
This limit value of the FA can be traduced in terms of an optimal \lth, 
where we obtain $\lambda_{opt}^V = 0.175$ for the V-web scheme and 
$\lambda_{opt}^T = 0.265$ for the T-web scheme, both values consistent 
with optimal thresholds normally taken in previous works \SRKED{[references]}. 
Due to the definition of the fractional anisotropy index, it presents the 
highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$.
Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
FA limit, such that the outer regions of voids becomes highly anisotropic, 
it would imply that voids are invading filaments and sheets, so the 
optimal \lth value is a limit value up to which we can have void regions. 
For other type of environment such as sheets, filaments and knots, the 
$\lambda_1$ eigenvalue does not control their spatial boundaries, so the 
correlation with the FA index is no longer valid beyond the threshold 
values, furthermore the larger dispersion of the FA distribution also 
indicates that contours of the FA field are no longer corresponding to 
contours of the $\lambda_1$ field. Nevertheless, for high $\lambda_1$ 
values, i.e. $\lambda_1>1.0$, the median value of the FA index decreases 
to lower values, indicating the presence of isotropic knots. All of this 
allows us to conclude that the distribution of the FA with respect to the 
$\lambda_1$ eigenvalue is not only an one-dimensional tomography of voids, 
but also a sort of one-dimensional projection of the global structure of 
the cosmic web, starting in highly isotropic central voids, passing 
through very anisotropic sheets and filaments, until isotropic knot 
regions.

@@

Once defined our method to classify bulk voids based upon web 
classification schemes of the cosmic web, we proceed to analyse some 
physical properties in order to compare their consistency with the 
geometry of voids as quantified by our method and by density-based schemes.
Next, through the reduced inertia tensor we quantify the shape distribution 
of voids. Finally, we compute numerical radial profiles of density and 
peculiar velocity of bulk voids.

%-------------------------------------------------------------------------
\subsection{Statistics of halos in voids}
\label{subsec:shape_voids}
%-------------------------------------------------------------------------

One of the main challenges in observational void finding is the discrete 
nature of galaxy surveys

 we calculate contours of discrete fields like the median mass and 
the local number of local dark matter halos and

, like the inertia values,
the density and peculiar velocities profiles as calculated over the grid 
and profiles of number of halos.
